Hardware-in-the-Loop Plant Modeling for Autonomous Vehicle

### 2021-11-12 proposalPres.tex
Updated simulation results figures
Updated proposalPres.tex

\begin{frame}
\begin{minipage}[t]{0.48\linewidth}
\tiny
	\begin{block}{System Inputs}
		\begin{itemize}
			\tiny
		    \item Steering Model
		    \begin{itemize}
		    \tiny
		    		\item Torque Voltages
		    		\begin{itemize}
		    		\tiny
		    			\item Desired Steering Wheel Angle
		    			\item Actual Steering Wheel Angle
		    		\end{itemize}
		    \end{itemize}
		    \item Acceleration Model
		    \begin{itemize}
		    \tiny
		    		\item Acceleration Pedal Voltages
		    \end{itemize}
		    \item Brake Model
		    \begin{itemize}
		    \tiny
		    		\item Brake Pedal Pressure Voltages
		    		\item Brake Pedal Stroke Voltages 
		    		\item Brake Pedal On/Off Switch
		    \end{itemize}
		    \item Shift Model
		    \begin{itemize}
		    \tiny
		    		\item Desired Shift Gear
		    \end{itemize}
		    \item Speed Model
		    \begin{itemize}
		    \tiny
		    		\item Acceleration Pedal Position
		    		\item Brake Pedal Position
		    		\item Shifter Actual Gear
		    \end{itemize}
		    \item Speed Control Model
		    \begin{itemize}
		    \tiny
		    		\item Desired Vehicle Speed
		    \end{itemize}
		\end{itemize}
	\end{block}
\end{minipage}%
\hfill%
\begin{minipage}[t]{0.48\linewidth}
\begin{block}{System Inputs}
		\begin{itemize}
			\tiny
		    \item Steering Model
		    \begin{itemize}
		    \tiny
		    		\item Wheel Angle
		    		\item Actual Steering Angle
		    \end{itemize}
		    \item Acceleration Model
		    \begin{itemize}
		    \tiny
		    		\item Acceleration Pedal Position
		    \end{itemize}
		    \item Brake Model
		    \begin{itemize}
		    \tiny
		    		\item Brake Pedal Position
		    		\item Brake Pressed
		    \end{itemize}
		    \item Shift Model
		    \begin{itemize}
		    \tiny
		    		\item Actual Shift Gear
		    \end{itemize}
		    \item Speed Model
		    \begin{itemize}
		    \tiny
		    		\item Vehicle Speed
		    \end{itemize}
		    \item Speed Control Model
		    \begin{itemize}
		    \tiny
		    		\item Vehicle Speed
		    \end{itemize}
		\end{itemize}
	\end{block}
\end{minipage}
\end{frame}

@@

%----------------------------------
\section{Simulation Results}

@@

@@

>>>>

\begin{frame}
\begin{minipage}[t]{0.48\linewidth}
\tiny
	\begin{block}{System Inputs}
		\begin{itemize}
			\tiny
		    \item Steering Model
		    \begin{itemize}
		    \tiny
		    		\item Torque Voltages
		    		\begin{itemize}
		    		\tiny
		    			\item Desired Steering Wheel Angle
		    			\item Actual Steering Wheel Angle
		    		\end{itemize}
		    \end{itemize}
		    \item Acceleration Model
		    \begin{itemize}
		    \tiny
		    		\item Acceleration Pedal Voltages
		    \end{itemize}
		    \item Brake Model
		    \begin{itemize}
		    \tiny
		    		\item Brake Pedal Pressure Voltages
		    		\item Brake Pedal Stroke Voltages 
		    		\item Brake Pedal On/Off Switch
		    \end{itemize}
		    \item Shift Model
		    \begin{itemize}
		    \tiny
		    		\item Desired Shift Gear
		    \end{itemize}
		    \item Speed Model
		    \begin{itemize}
		    \tiny
		    		\item Acceleration Pedal Position
		    		\item Brake Pedal Position
		    		\item Shifter Actual Gear
		    \end{itemize}
		    \item Speed Control Model
		    \begin{itemize}
		    \tiny
		    		\item Desired Vehicle Speed
		    \end{itemize}
		\end{itemize}
	\end{block}
\end{minipage}%
\hfill%
\begin{minipage}[t]{0.48\linewidth}
\begin{block}{System Outputs}
		\begin{itemize}
			\tiny
		    \item Steering Model
		    \begin{itemize}
		    \tiny
		    		\item Wheel Angle
		    		\item Actual Steering Angle
		    \end{itemize}
		    \item Acceleration Model
		    \begin{itemize}
		    \tiny
		    		\item Acceleration Pedal Position
		    \end{itemize}
		    \item Brake Model
		    \begin{itemize}
		    \tiny
		    		\item Brake Pedal Position
		    		\item Brake Pressed
		    \end{itemize}
		    \item Shift Model
		    \begin{itemize}
		    \tiny
		    		\item Actual Shift Gear
		    \end{itemize}
		    \item Speed Model
		    \begin{itemize}
		    \tiny
		    		\item Vehicle Speed
		    \end{itemize}
		    \item Speed Control Model
		    \begin{itemize}
		    \tiny
		    		\item Vehicle Speed
		    \end{itemize}
		\end{itemize}
	\end{block}
\end{minipage}
\end{frame}

@@

%----------------------------------
\subsection{Modeling}

\begin{frame}{Model Equations}
	\begin{block}{}
		\begin{itemize}
			\item Transfer Function Model: 
			\begin{equation}
				\frac{Y(s)}{U_A(s)} = \frac{b_{n}*s^{n} + b_{n-1}*s^{n-1} + ... + b_1*s + b_0}{a_{m}*s^{m} + a_{m-1}*s^{m-1} + ... + a_1*s + a_0}
			\end{equation}
			where m = number of poles and n = number of zeros
			\item ARX Model: 
			\begin{equation}
				A(z)*y(t) = B(z)*u(t) + e(t)
			\end{equation}
		\end{itemize}
	\end{block}
\end{frame}

%----------------------------------
\section{Validation and Testing}

@@

\begin{frame}{By-Wire Steering System Transfer Function}
\begin{minipage}[t]{0.48\linewidth}
	\begin{block}{Torque A}
		\tiny
		\begin{tabular}{ cc }   % top level tables, with 2 columns
			% leftmost table of the top level table
			\begin{tabular}{ |c|c| } 
				\hline
				b_0 & 3.44E-16 \\
				b_1 & -2.203E-15 \\
				b_2 & 1.24E-13 \\
				b_3 & 5.975E-13 \\
				b_4 & 3.001E-12 \\
				b_5 & 5.23E-12 \\
				\hline
			\end{tabular} &  % starting rightmost sub table
			% table 2
			\begin{tabular}{ |c|c| } 
				\hline
				a_0 & 1.949E-16 \\
				a_1 & 1.455E-14 \\
				a_2 & 8.797E-13 \\
				a_3 & 2.304E-11 \\
				a_4 & 9.041E-10 \\
				a_5 & 9.01E-9 \\
				a_6 & 2.714E-7 \\
				a_7 & 9.241E-7 \\
				a_8 & 1.946E-5 \\
				a_9 & 3.889E-5 \\
				a_{10} & 0.0005721 \\
				a_{11} & 0.0008035 \\
				a_{12} & 0.008695 \\
				a_{13} & 0.008922 \\
				a_{14} & 0.07499 \\
				a_{15} & 0.05422 \\
				a_{16} & 0.3631 \\
				a_{17} & 0.1693 \\
				a_{18} & 0.9394 \\
				a_{19} & 0.2118 \\
				a_{20} & 1 \\
				\hline
			\end{tabular} \\
		\end{tabular}
	\end{block}
\end{minipage}%
\hfill%
\begin{minipage}[t]{0.48\linewidth}
	\begin{block}{Torque B}
		\tiny
		\begin{tabular}{ cc }   % top level tables, with 2 columns
			% leftmost table of the top level table
			\begin{tabular}{ |c|c| } 
				\hline
				b_0 & -6.645E-15 \\
				b_1 & 2.161E-14 \\
				b_2 & -2.605E-14 \\
				b_3 & -4.744E-13 \\
				b_4 & -1.813E-13 \\
				b_5 & -4.858E-12 \\
				\hline
			\end{tabular} &  % starting rightmost sub table
			% table 2
			\begin{tabular}{ |c|c| } 
				\hline
				a_0 & 2.92E-15 \\
				a_1 & 2.758E-13 \\
				a_2 & 1.761E-11 \\
				a_3 & 4.228E-10 \\
				a_4 & 1.422E-8 \\
				a_5 & 1.561E-7 \\
				a_6 & 1.501E-6 \\
				a_7 & 8.426E-6 \\
				a_8 & 5.981E-5 \\
				a_9 & 0.0002016 \\
				a_{10} & 0.001226 \\
				a_{11} & 0.002649 \\
				a_{12} & 0.01456 \\
				a_{13} & 0.02044 \\
				a_{14} & 0.104 \\
				a_{15} & 0.09228 \\
				a_{16} & 0.4417 \\
				a_{17} & 0.2257 \\
				a_{18} & 1.025 \\
				a_{19} & 0.2305 \\
				a_{20} & 1 \\
				\hline
			\end{tabular} \\
		\end{tabular}
	\end{block}
\end{minipage}
\end{frame}

\begin{frame}{Manual Steering System Transfer Function}
\begin{minipage}[t]{0.48\linewidth}
	\begin{block}{Torque A}
		\tiny
		\begin{tabular}{ cc }   % top level tables, with 2 columns
			% leftmost table of the top level table
			\begin{tabular}{ |c|c| } 
				\hline
				b_0 & 6.516E4 \\
				b_1 & -2.944E5 \\
				b_2 & 2.328E5 \\
				b_3 & -2.487E5 \\
				b_4 & 8.25E4 \\
				b_5 & -3.038E4 \\
				\hline
			\end{tabular} &  % starting rightmost sub table
			% table 2
			\begin{tabular}{ |c|c| } 
				\hline
				a_0 & 1.224E5 \\
				a_1 & 4.227E5 \\
				a_2 & 2.202E6 \\
				a_3 & 3.54E6 \\
				a_4 & 7.98E6 \\
				a_5 & 7.62E5 \\
				a_6 & 1.071E7 \\
				a_7 & 6.745E6 \\
				a_8 & 6.85E6 \\
				a_9 & 3.006E6 \\
				a_{10} & 2.365E6 \\
				a_{11} & 7.37E5 \\
				a_{12} & 4.669E5 \\
				a_{13} & 1.021E5 \\
				a_{14} & 5.319E4 \\
				a_{15} & 7752 \\
				a_{16} & 3353 \\
				a_{17} & 287.5 \\
				a_{18} & 102.4 \\
				a_{19} & 3.653 \\
				a_{20} & 1 \\
				\hline
			\end{tabular} \\
		\end{tabular}
	\end{block}
\end{minipage}%
\hfill%
\begin{minipage}[t]{0.48\linewidth}
	\begin{block}{Torque B}
		\tiny
		\begin{tabular}{ cc }   % top level tables, with 2 columns
			20th Order Transfer Function Model			
			% leftmost table of the top level table
			\begin{tabular}{ |c|c| } 
				\hline
				b_0 & 1.209E4 \\
				b_1 & 1.855E5 \\
				b_2 & -2.801E5 \\
				b_3 & 4.72E5 \\
				b_4 & -3.976E4 \\
				b_5 & 7.693E4 \\
				\hline
			\end{tabular} &  % starting rightmost sub table
			% table 2
			\begin{tabular}{ |c|c| } 
				\hline
				a_0 & 4.687E4 \\
				a_1 & 7.037E5 \\
				a_2 & 2.624E6 \\
				a_3 & 6.133E6 \\
				a_4 & 1.197E7 \\
				a_5 & 1.487E7 \\
				a_6 & 1.887E7 \\
				a_7 & 1.446E7 \\
				a_8 & 1.314E7 \\
				a_9 & 7.01E6 \\
				a_{10} & 4.79E6 \\
				a_{11} & 1.886E6 \\
				a_{12} & 9.836E5 \\
				a_{13} & 2.937E5 \\
				a_{14} & 1.149E5 \\
				a_{15} & 2.617E4 \\
				a_{16} & 7205 \\
				a_{17} & 1232 \\
				a_{18} & 200 \\
				a_{19} & 23.54 \\
				a_{20} & 1 \\
				\hline
			\end{tabular} \\
		\end{tabular}
	\end{block}
\end{minipage}
\end{frame}

@@

\begin{frame}{By-Wire Acceleration System Transfer Function}
	\begin{block}{Fourth-Order ARX Model}
		\begin{equation}
			A(z)*y(t) = B(z)*u(t) + e(t)
		\end{equation}
		%
		where, 
		%
		\begin{equation}
			A(z) = 1 - 1.018*z^{-1} - 0.002901*z^{-2} + 0.4631*z^{-3} - 0.2038*z^{-4}
		\end{equation}
		\begin{equation}
			B_1(z) = -0.0207 - 0.01912*z^{-1} - 0.02159*z^{-2} - 0.03307*z^{-3}
		\end{equation}
		\begin{equation}
			B_2(z) = 0.02017 + 0.01833*z^{-1} + 0.09461*z^{-2} + 0.05683*z^{-3}
		\end{equation}
	\end{block}
\end{frame}

\begin{frame}{Manual Acceleration System Transfer Function}
\begin{minipage}[t]{0.48\linewidth}
	\begin{block}{Torque A}
		\tiny
		\begin{tabular}{ cc }   % top level tables, with 2 columns
			% leftmost table of the top level table
			\begin{tabular}{ |c|c| } 
				\hline
				b_0 & -5.741E6 \\
				b_1 & -2.644E7 \\
				b_2 & -2.797E6 \\
				b_3 & -1.304E7 \\
				b_4 & -3.203E6 \\
				b_5 & -1.159E6 \\
				b_6 & -5.519E5 \\
				\hline
			\end{tabular} &  % starting rightmost sub table
			% table 2
			\begin{tabular}{ |c|c| } 
				\hline
				a_0 & 2.307E7 \\
				a_1 & 8.369E7 \\
				a_2 & 9.137E8 \\
				a_3 & 1.992E9 \\
				a_4 & 3.753E9 \\
				a_5 & 5.454E9 \\
				a_6 & 5.548E9 \\
				a_7 & 5.869E9 \\
				a_8 & 3.453E9 \\
				a_9 & 3.161E9 \\
				a_{10} & 1.54E9 \\
				a_{11} & 9.654E8 \\
				a_{12} & 3.556E8 \\
				a_{13} & 1.789E8 \\
				a_{14} & 5.082E7 \\
				a_{15} & 2.071E7 \\
				a_{16} & 4.569E6 \\
				a_{17} & 1.498E6 \\
				a_{18} & 2.553E5 \\
				a_{19} & 6.532E4 \\
				a_{20} & 8443 \\
				a_{21} & 1559 \\
				a_{22} & 147.3 \\
				a_{23} & 15.5 \\
				a_{24} & 1 \\
				\hline
			\end{tabular} \\
		\end{tabular}
	\end{block}
\end{minipage}%
\hfill%
\begin{minipage}[t]{0.48\linewidth}
	\begin{block}{Torque B}
		\tiny
		\begin{tabular}{ cc }   % top level tables, with 2 columns
			% leftmost table of the top level table
			\begin{tabular}{ |c|c| } 
				\hline
				b_0 & -4.159E6 \\
				b_1 & 1.851E6 \\
				b_2 & -4.457E6 \\
				b_3 & 9.043E5 \\
				b_4 & -7.45E5 \\
				b_5 & 1.865E5 \\
				b_6 & -1.545E4 \\
				\hline
			\end{tabular} &  % starting rightmost sub table
			% table 2
			\begin{tabular}{ |c|c| } 
				\hline
				a_0 & 5.224E6 \\
				a_1 & 4.205E7 \\
				a_2 & 1.429E8 \\
				a_3 & 3.233E8 \\
				a_4 & 5.444E8 \\
				a_5 & 7.326E8 \\
				a_6 & 8.247E8 \\
				a_7 & 7.402E8 \\
				a_8 & 6.301E8 \\
				a_9 & 3.99E8 \\
				a_{10} & 2.731E8 \\
				a_{11} & 1.264E8 \\
				a_{12} & 7.223E7 \\
				a_{13} & 2.48E7 \\
				a_{14} & 1.216E7 \\
				a_{15} & 3.084E6 \\
				a_{16} & 1.324E6 \\
				a_{17} & 2.422E5 \\
				a_{18} & 9.264E4 \\
				a_{19} & 1.159E4 \\
				a_{20} & 4003 \\
				a_{21} & 307.4 \\
				a_{22} & 96.87 \\
				a_{23} & 3.451 \\
				a_{24} & 1 \\
				\hline
			\end{tabular} \\
		\end{tabular}
	\end{block}
\end{minipage}
\end{frame}
